---
title: 'Reproducible Research: Peer Assessment 1'
output:
  html_document:
    keep_md: yes
  word_document: default
---
##Setup  

```{r}
library("dplyr")
library("markdown")
filez<-"activity.zip"
filec<-"activity.csv"
```

## Loading and preprocessing the data 

###Extracting the data file from the zip file  

```{r}
unzip(filez)
```

###Reading the data  

```{r}
data<-read.csv(filec)
```

###Filter lines with missing values  

```{r}
data<-data[complete.cases(data),]
```

## What is mean total number of steps taken per day?

###Sumarize data per day  

```{r}
suma<-summarise(group_by(data, date), sum(steps))
names(suma)<-c("date", "stepsum")
stepmn<-mean(suma$stepsum)
stepmd<-median(suma$stepsum)
```

The mean number of steps per day is `r stepmn`  and the median `r stepmd`.  

###plot Histogram of total number of step taken each day  

```{r}
hist(suma$stepsum)
```

## What is the average daily activity pattern?  

```{r}
inter<-summarise(group_by(data, interval), mean(steps))
names(inter)<-c("interval", "stepsmean")
plot(inter$interval,inter$stepsmean, type="l")
```

###Interval with maximum of steps  

```{r}
maxi<-max(inter$stepsmean)
maxinter<-inter[inter$stepsmean==maxi,1]

```
The maximun average of steps is `r maxi` and takes place during interval `r maxinter`.  


## Imputing missing values

```{r}
data<-read.csv(filec)
missval<-sum(is.na(data$steps))
```

The number of missing values is `r missval`.  

An inner join and for next with and ifelse are used to convert  
all the NAs to the value of the mean of the steps for that interval.

```{r}
datamiss<-inner_join(data, inter)
for(i in 1:length(datamiss$steps)){
        ifelse(is.na(datamiss$steps[i]), datamiss$steps[i]<-datamiss$stepsmean[i], datamiss$stepsmean[i]<-0)       
}
sumamiss<-summarise(group_by(datamiss, date), sum(steps))
names(sumamiss)<-c("date", "stepsum")
stepmn<-mean(sumamiss$steps)
stepmd<-median(sumamiss$steps)
```

The mean number of steps per day is `r stepmn`  and the median `r stepmd`.  

###plot Histogram of total number of step taken each day 

```{r}
hist(sumamiss$stepsum)
```



## Are there differences in activity patterns between weekdays and weekends?
